Flow-Based Cost Allocation in Linear Optimized Power Systems are non-unique but localizable

### 2020-08-17 paper/flow_based.tex
adjust examples plot
adjust shadowprice for branches properly

In order to take already built infrastructure into account, the capacity $\capacity$ can be constrained to a minimum required capacity $\capacitylower$. Mathematically this translates to 
\begin{align}
    \capacitylower - \capacity  \le 0 \resultsin{\mulowernom} \hpad \forall{i \in I}
\label{eq:capacityexpansionminimum}
\end{align}
Again, such a setup alters the zero profit condition of asset $i$ as soon as the constraint becomes binding. 
In that case, asset $i$ does not collect enough revenue in order to match the CAPEX by a difference is given by 
\begin{align}
    \remainingcost_i = \mulowernom \capacity
    \Forall{i}
\end{align}
% In order to take this effect into account for the cost allocation, we update the cost factors in \cref{tab:cost_allocation_map} to

@@

>>>>

In order to take already built infrastructure into account, the capacity $\capacity$ can be constrained to a minimum required capacity $\capacitylower$. Mathematically this translates to 
\begin{align}
    \capacitylower - \capacity  \le 0 \resultsin{\mulowernom} \hpad \forall{i \in I}
\label{eq:capacityexpansionminimum}
\end{align}
Again, such a setup alters the zero profit condition of asset $i$ as soon as the constraint becomes binding. 
In that case, asset $i$ does not collect enough revenue in order to match the CAPEX. The difference is given by 
\begin{align}
    \remainingcost_i = \mulowernom \capacity
    \Forall{i}
\end{align}
Again, we can balance this effect out by updating the cost factor to 
\begin{align}
    \costfactor \rightarrow \costfactor + 
\end{align}

% In order to take this effect into account for the cost allocation, we update the cost factors in \cref{tab:cost_allocation_map} to

@@

We apply the cost allocation on a German power system model
